---
title: "LDF Method Example"
author: "CLRS Concurrent Session #___"
date: "Thursday, September 10, 2015"
output: html_document
---

# Estimate ultimate loss from the RAA data

Load the ChainLadder package and view the RAA triangle.

```{r}
suppressPackageStartupMessages(library(ChainLadder))
RAA
```

Form the triangle of age-to-age factors and 
initially select the weighted average link ratios.

```{r}
ataRAA <- ata(RAA)
ataRAA
selectedATA <- round(attr(ataRAA, "vwtd"), 3)
selectedATA
```

## Analyze Tail

The average link ratios seem to follow a pattern.

```{r}
plot(log(selectedATA - 1))
x <-1:9
y <- log(selectedATA - 1)
lm(y~x)
abline(lm(y~x))
```

Assuming the pattern continues,
what magnitude of tail is implied? 
Investigate the next 10 years versus the next 100 years.

```{r}
age <- 10:19
tail(cumprod(exp(0.9045 - 0.6340 * age) + 1), 1)
```

Over the next 100 years, 
the tail would be
`r tail(cumprod(exp(0.9045 - 0.6340 * 10:109) + 1), 1)`.

The selected tail is therefore 1.01.
In addition, select the simple average link ratio for the 1-2 period.
Here is the cumulative loss development pattern:

``` {r, echo = FALSE}
tail = 1.01
selectedATA[1] <- attr(ataRAA, 'smpl')[1]
CDF <- round(cumprod(rev(c(selectedATA, tail))), 3)
CDF
```

## Project to ultimate

Here is the loss development estimate with those selections and a total:

``` {r}
LDEst <- data.frame(Latest = getLatestCumulative(RAA), CDF, 
                    Ultimate = round(getLatestCumulative(RAA) * CDF, 0))
Total <- colSums(LDEst)
Total[2] <- NA
rbind(LDEst, Sum = Total)
```

