---
title: "Analysis of RAA loss data"
author: "CLRS Concurrent Session"
date: "Thursday, September 10, 2015"
output: pdf_document
---

Load the ChainLadder package and view the RAA triangle.

```{r message=FALSE}
library(ChainLadder)
RAA
```

Form the triangle of age-to-age factors and initially select the weighted average link ratios.

```{r echo = FALSE}
ataRAA <- ata(RAA)
ataRAA
selectedATA <- round(attr(ataRAA, "vwtd"), 3)
selectedATA
```

## Analyze tail

The average link ratios seem to follow a pattern.

```{r echo=FALSE}
age <- 1:9
logLDF <- log(selectedATA - 1)
plot(age, logLDF)
fit <- lm(logLDF ~ age)
abline(fit)

summary(fit)
```

Assuming the pattern continues, what magnitude of tail is implied? 
Investigate the next 10 years versus the next 100 years.

```{r echo=FALSE}
moreAges <- data.frame(age = 10:19)
moreLDF <- predict(fit, newdata = moreAges, type = "response")

tail_10 <- prod(exp(moreLDF) + 1)

moreAges <- data.frame(age = 10:109)
LDF_100 <- predict(fit, newdata = moreAges, type = "response")

tail_100 <- prod(exp(LDF_100) + 1)
```

Over the next 100 years, the tail would be `r tail_100`. We use this as our estimated tail factor.

In addition, select the simple average link ratio for the 1-2 period.
Here is the cumulative loss development pattern:

``` {r, echo = FALSE}
tail = tail_100
selectedATA[1] <- attr(ataRAA, 'smpl')[1]
CDF <- round(cumprod(rev(c(selectedATA, tail))), 3)
CDF
```

## Project to ultimate

``` {r echo=FALSE}
LDEst <- data.frame(Latest = getLatestCumulative(RAA), CDF, 
                    Ultimate = round(getLatestCumulative(RAA) * CDF, 0))
Total <- colSums(LDEst)
Total[2] <- NA
rbind(LDEst, Sum = Total)
```
